---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RLeadfeeder

<!-- badges: start -->
[![R-CMD-check](https://github.com/henrywangnl/RLeadfeeder/workflows/R-CMD-check/badge.svg)](https://github.com/henrywangnl/RLeadfeeder/actions)
<!-- badges: end -->

The goal of RLeadfeeder is to let you work with [Leadfeeder](https://www.leadfeeder.com/) API.

## Installation

```r
remotes::install_github("henrywangnl/RLeadfeeder")
```


## Authentication

Leadfeeder API expects an API token to be included in all requests sent to the server.

You can generate your unique authentication token at [Leadfeeder API settings](https://app.leadfeeder.com/l/settings/personal/api-tokens).


```{r example}
library(RLeadfeeder)

## Set your Leadfeeder API token
set_token(token = "YOUR_API_TOKEN")

## Check your Leadfeeder API token
get_token()
```

## Get accounts

Retrieve all accounts that you have access to.

```{r accounts, eval=FALSE}
get_accounts()
```

## Get feeds

Get all the feeds for an Account.

```{r feeds, eval=FALSE}
get_feeds(account_id = "12345")
```

## Get leads

Retrieve a list of leads in an Account on a specific time interval. The total number of results is limited to the first 10000 leads.

```{r leads, eval=FALSE}
get_leads(
  account_id = "12345", 
  start_date = "2020-11-01", 
  end_date = "2020-11-30"
)
```

## Get visits

Retrieve a list of Visits for all Leads from a specific time interval.

```{r visits, eval=FALSE}
get_visits(
   account_id = "12345", 
   start_date = "2020-11-01", 
   end_date = "2020-11-30"
)
```

